Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-06 talk/pepm2011/paper.tex
re-copy formulas from lyx file

\begin{figure*}
\begin{center}
\begin{tabular}{lc}
\emph{new} & ${\displaystyle \frac{v^{*}\,\mathrm{fresh}}{v=\mathrm{new}(T),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle \,\right\rangle ,E\left[v\mapsto v^{*}\right],S\left[v^{*}\mapsto\left(T,\mathrm{null,null}\right)\right]}}$\tabularnewline[3em]
\emph{get} & ${\displaystyle \frac{E(u)\in\mathrm{dom}(S)}{v=\mathrm{get}(u,F),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle \,\right\rangle ,E\left[v\mapsto S(E(u))_{F}\right],S}}$\tabularnewline[3em]
 & ${\displaystyle \frac{E(u)\notin\mathrm{dom}(S)\, v^{*}\,\mathrm{fresh}}{v=\mathrm{get}(u,F),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle v^{*}=\mathrm{get}(E(u),F)\right\rangle ,E\left[v\mapsto v^{*}\right],S}}$\tabularnewline[3em]
\emph{set} & ${\displaystyle \frac{E(v)\in\mathrm{dom}(S)}{\mathrm{set}\left(v,F,u\right),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle \,\right\rangle ,E,S\left[E\left(v\right)\mapsto\left(S(E(v))!_{F}E(u)\right)\right]}}$\tabularnewline[3em]
 & ${\displaystyle \frac{E(v)\notin\mathrm{dom}\left(S\right),\,\left(E(v),S\right)\overset{\mathrm{lift}}{\Longrightarrow}\left(\mathrm{ops},S^{\prime}\right)}{\mathrm{set}\left(v,F,u\right),E,S\overset{\mathrm{opt}}{\Longrightarrow}\mathrm{ops}::\left\langle \mathrm{set}\left(E(v),F,E(u)\right)\right\rangle ,E,S^{\prime}}}$\tabularnewline[3em]
\emph{guard} & ${\displaystyle \frac{E(v)\in\mathrm{dom}(S),\,\mathrm{type}(S(E(v)))=T}{\mathrm{guard}(v,T),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle \,\right\rangle ,E,S}}$\tabularnewline[3em]
 & ${\displaystyle \frac{E(v)\in\mathrm{dom}(S),\,\mathrm{type}(S(E(v)))\neq T,\,\left(E(v),S\right)\overset{\mathrm{lift}}{\Longrightarrow}\left(\mathrm{ops},S^{\prime}\right)}{\mathrm{guard}(v,T),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle \mathrm{guard}(E\left(v\right),T)\right\rangle ,E,S^{\prime}}}$\tabularnewline[3em]
 & ${\displaystyle \frac{E(v)\notin\mathrm{dom}(S)}{\mathrm{guard}(v,T),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle \mathrm{guard}(E\left(v\right),T)\right\rangle ,E,S}}$\tabularnewline[3em]
\emph{lifting} & ${\displaystyle \frac{v^{*}\notin\mathrm{dom}(S)}{v^{*},S\overset{\mathrm{lift}}{\Longrightarrow}\left\langle \,\right\rangle ,S}}$\tabularnewline[3em]
 & ${\displaystyle \frac{v^{*}\in\mathrm{dom}(S),\,\left(v^{*},S\setminus\left\{ v^{*}\mapsto S\left(v^{*}\right)\right\} \right)\overset{\mathrm{liftfields}}{\Longrightarrow}\left(\mathrm{ops},S^{\prime}\right)}{v^{*},S\overset{\mathrm{lift}}{\Longrightarrow}\left\langle v^{*}=\mathrm{new}\left(T\right)\right\rangle ::ops,S^{\prime}}}$\tabularnewline[3em]
 & ${\displaystyle
 \frac{\left(S\left(v^{*}\right)_{L},S\right)\overset{\mathrm{lift}}{\Longrightarrow}\left(\mathrm{ops}_{L},S^{\prime}\right),\,\left(S\left(v^{*}\right)_{R},S^{\prime}\right)\overset{\mathrm{lift}}{\Longrightarrow}\left(\mathrm{ops}_{R},S^{\prime\prime}\right)}{v^{*},S\overset{\mathrm{liftfields}}{=\!=\!\Longrightarrow}\mathrm{ops}_{L}::ops_{R}::\left\langle
 \mathrm{set}\left(v^{*},L,S\left(v^{*}\right)_{L}\right),\,\mathrm{set}\left(v^{*},R,S\left(v^{*}\right)_{R}\right)\right\rangle ,S^{\prime}}}$\tabularnewline[3em]
\end{tabular}

>>>>

\begin{figure*}
\begin{center}
\begin{tabular}{lc}
\emph{new} & ${\displaystyle \frac{v^{*}\,\mathrm{fresh}}{v=\mathrm{new}(T),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle \,\right\rangle ,E\left[v\mapsto v^{*}\right],S\left[v^{*}\mapsto\left(T,\mathrm{null,null}\right)\right]}}$\tabularnewline[3em]
\emph{get} & ${\displaystyle \frac{E(u)\in\mathrm{dom}(S)}{v=\mathrm{get}(u,F),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle \,\right\rangle ,E\left[v\mapsto S(E(u))_{F}\right],S}}$\tabularnewline[3em]
 & ${\displaystyle \frac{E(u)\notin\mathrm{dom}(S)\, v^{*}\,\mathrm{fresh}}{v=\mathrm{get}(u,F),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle v^{*}=\mathrm{get}(E(u),F)\right\rangle ,E\left[v\mapsto v^{*}\right],S}}$\tabularnewline[3em]
\emph{set} & ${\displaystyle \frac{E(v)\in\mathrm{dom}(S)}{\mathrm{set}\left(v,F,u\right),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle \,\right\rangle ,E,S\left[E\left(v\right)\mapsto\left(S(E(v))!_{F}E(u)\right)\right]}}$\tabularnewline[3em]
 & ${\displaystyle \frac{E(v)\notin\mathrm{dom}\left(S\right),\,\left(E(v),S\right)\overset{\mathrm{lift}}{\Longrightarrow}\left(\mathrm{ops},S^{\prime}\right)}{\mathrm{set}\left(v,F,u\right),E,S\overset{\mathrm{opt}}{\Longrightarrow}\mathrm{ops}::\left\langle \mathrm{set}\left(E(v),F,E(u)\right)\right\rangle ,E,S^{\prime}}}$\tabularnewline[3em]
\emph{guard} & ${\displaystyle \frac{E(v)\in\mathrm{dom}(S),\,\mathrm{type}(S(E(v)))=T}{\mathrm{guard}(v,T),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle \,\right\rangle ,E,S}}$\tabularnewline[3em]
 & ${\displaystyle \frac{E(v)\notin\mathrm{dom}(S)\vee\mathrm{type}(S(E(v)))\neq T,\,\left(E(v),S\right)\overset{\mathrm{lift}}{\Longrightarrow}\left(\mathrm{ops},S^{\prime}\right)}{\mathrm{guard}(v,T),E,S\overset{\mathrm{opt}}{\Longrightarrow}\left\langle \mathrm{guard}(E\left(v\right),T)\right\rangle ,E,S^{\prime}}}$\tabularnewline[3em]
\emph{lifting} & ${\displaystyle \frac{v^{*}\notin\mathrm{dom}(S)}{v^{*},S\overset{\mathrm{lift}}{\Longrightarrow}\left\langle \,\right\rangle ,S}}$\tabularnewline[3em]
 & ${\displaystyle \frac{v^{*}\in\mathrm{dom}(S),\,\left(v^{*},S\right)\overset{\mathrm{liftfields}}{=\!=\!\Longrightarrow}\left(\mathrm{ops},S^{\prime}\right)}{v^{*},S\overset{\mathrm{lift}}{\Longrightarrow}\left\langle v^{*}=\mathrm{new}\left(T\right)\right\rangle ::ops,S^{\prime}}}$\tabularnewline[3em]
 & ${\displaystyle \frac{\left(S\left(v^{*}\right)_{L},S\setminus\left\{ v^{*}\mapsto S\left(v^{*}\right)\right\} \right)\overset{\mathrm{lift}}{\Longrightarrow}\left(\mathrm{ops}_{L},S^{\prime}\right),\,\left(S\left(v^{*}\right)_{R},S^{\prime}\right)\overset{\mathrm{lift}}{\Longrightarrow}\left(\mathrm{ops}_{R},S^{\prime\prime}\right)}{v^{*},S\overset{\mathrm{liftfields}}{=\!=\!\Longrightarrow}\mathrm{ops}_{L}::ops_{R}::\left\langle \mathrm{set}\left(v^{*},L,S\left(v^{*}\right)_{L}\right),\,\mathrm{set}\left(v^{*},R,S\left(v^{*}\right)_{R}\right)\right\rangle ,S^{\prime}}}$\tabularnewline[3em]
\end{tabular}
